Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-01 ms.tex
fill in W2 SGC figure caption

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w2_large_scale.eps, width=7.0in}
  \caption{\label{fig:w2_large} A large portion of the south Galactic
           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. It is clear that the scattered
           moonlight has been largely removed in W2, although 
           some traces still remain.}
 \end{center}
\end{figure*}
% should state approximate bounding coords in terms of lambda, beta

@@

% figure showing before/after of SGP on large scales in both W1/W2

>>>>

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w2_large_scale.eps, width=7.0in}
  \caption{\label{fig:w2_large} A large portion of the south Galactic
           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. It is clear that the scattered
           moonlight, which appears as a series of vertical streaks, has been 
           largely removed in W2, although some traces still remain. The
           two dotted red boxes show locations where Jupiter passed through
           the WISE field of view. The imprints of such planet sightings have 
           now been removed.}
 \end{center}
\end{figure*}
% should state approximate bounding coords in terms of lambda, beta

@@
